An Empirical Analysis of the Role of Energy in Economic Growth

### 2014-01-01 EconGrowth2.Rnw
Fixed height of one figure.

<<CES_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8, fig.cap="CES fitted models.">>=
spagData <- loadCESSpaghettiGraphData(energyType="Q", nest="all")
cesSpaghettiGraph(data=spagData, facet_formula=Country~nest, level=spaghettiGraphLevel)+
    labs(y="Indexed GDP (1980=1 or 1991=1)")
@

>>>>

<<CES_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="CES fitted models.">>=
spagData <- loadCESSpaghettiGraphData(energyType="Q", nest="all")
cesSpaghettiGraph(data=spagData, facet_formula=Country~nest, level=spaghettiGraphLevel)+
    labs(y="Indexed GDP (1980=1 or 1991=1)")
@
